Analyzing the impact of social attributes on commit integration success

### 2017-03-24 Paper/MSRChallenge2017.tex
hanged author order based on Claire's response

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{\IEEEauthorblockN{Zack Coker,
Mauricio Soto and
Claire Le Goues}
\IEEEauthorblockA{School of Computer Science\\
Carnegie Mellon University,
Pittsburgh PA\\ 
zfc@cs.cmu.edu, mauriciosoto@cmu.edu, clegoues@cs.cmu.edu}
}

>>>>

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{\IEEEauthorblockN{
Mauricio Soto, Zack Coker, and
Claire Le Goues}
\IEEEauthorblockA{School of Computer Science\\
Carnegie Mellon University,
Pittsburgh PA\\ 
mauriciosoto@cmu.edu, zfc@cs.cmu.edu, clegoues@cs.cmu.edu}
}
